A statistical framework for analysing whole-genome bisulfite-sequencing data

### 2015-05-04 Rmarkdown/wgbs_statistical_framework.Rmd
Add missing Ziller strand correlations data

@@

```{r Ziller_merged_strand_correlations, echo = FALSE, eval = TRUE, message = FALSE, results = "asis"}
x <- read.table("../data/strand_correlation/Ziller_merged_strand_correlations.txt",
stringsAsFactors = FALSE)
colnames(x) <- 1:10
xt <- xtable(x, caption = c("Correlations of $\\beta$-values across strands for the \\emph{Ziller} dataset. Each row is a sample and each column is a minimum coverage cutoff.", "\\emph{Ziller}: Correlations of $\\beta$-values across strands"), label = "tab:Ziller_merged_strand_correlations")
align(xt) <- rep("c", ncol(x) + 1)
digits(xt) <- 2
print(xt, booktabs = TRUE, comment = FALSE, tabular.environment = "longtable", floating = FALSE, caption.placement = 'top')
```

>>>>

```{r Ziller_merged_strand_correlations, echo = FALSE, eval = TRUE, message = FALSE, results = "asis"}
x <- read.table("../data/strand_correlation/Ziller_strand_correlations.txt",
stringsAsFactors = FALSE)
colnames(x) <- 1:10
xt <- xtable(x, caption = c("Correlations of $\\beta$-values across strands for the \\emph{Ziller} dataset. Each row is a sample and each column is a minimum coverage cutoff.", "\\emph{Ziller}: Correlations of $\\beta$-values across strands"), label = "tab:Ziller_merged_strand_correlations")
align(xt) <- rep("c", ncol(x) + 1)
digits(xt) <- 2
print(xt, booktabs = TRUE, comment = FALSE, tabular.environment = "longtable", floating = FALSE, caption.placement = 'top')
```

@@
